Research Cases

### 2025-10-14 Code/R/Research/cases_research.Rmd
Add complex mssa support

pred_mssa_rec <- function() {
  noise <- rnorm(N * P, 0, sd)
  x <- signal + noise
  rec <- reconstruct(ssa(x, L = L_mssa, kind = 'mssa'), groups = groups_mssa)
  Reduce("+", rec)
}

@@

if (n_case == "") {
  Ls_mssa <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 2)
} else {
  Ls_mssa <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 10)
}

@@

Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 2)

@@

```{r}
R <- 500

ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
hossa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
save(ssa_err, hossa_err, file = paste0("./comp_results/cases_errors/two_periodics", full_case, ".RData"))
```

@@

```{r}
print_errors(hossa_err)
summarise_errors(hossa_err)
```

>>>>

pred_mssa_rec <- function() {
  noise <- rnorm(N * P, 0, sd)
  x <- signal + noise
  # rec <- reconstruct(ssa(x, L = L_mssa, kind = 'mssa'), groups = groups_mssa)
  rec <- cmssa_reconstruct(x, L = L_mssa, groups = groups_mssa)
  Reduce("+", rec)
}

@@

if (n_case == "") {
  Ls_mssa <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 2)
  Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 2)
} else {
  Ls_mssa <- seq(from = max.r + 1,
                to = N - max.r - 1,
                by = 10)
  Ls_homssa = seq(from = max.r + 1,
                to = (N + 1) %/% 2,
                by = 10)
}

@@

@@

```{r}
R <- 2

if (is.matrix(signal)) {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_mssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_homssa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./comp_results/cases_errors/two_periodics_mv", full_case, ".RData"))
} else {
  ssa_err <- calc_errors_by_params(params_grid_ssa, R, pred_ssa_rec, rmse_ts_nd, signal, seed = 5)
  tssa_err <- calc_errors_by_params(params_grid_hossa, R, pred_hossa_rec, rmse_ts_nd, signal, seed = 5)
  save(ssa_err, tssa_err, file = paste0("./comp_results/cases_errors/two_periodics", full_case, ".RData"))
}
```

@@

```{r}
print_errors(tssa_err)
summarise_errors(tssa_err)
```
